The pollination trade-off

### 2018-11-15 paper/manuscript.Rmd
Swap order of predictors methods

Our second objetive is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the plants functional originality, and (*iv*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them. 
Here, we define visit efectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.

@@

To obtain data about (*i*) the number of shared pollinators for each species we pooled data from quantitative and qualitative polination networks. 
Qualitative networks were constructed based on two hour observations of floral visits in each fragment. 
Quantitative networks were constructed using two 50 m randomly located transects in each transect. 
We counted and collected all floral visitors found in a 2 m wide strip while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999]. 
We visited the transects each month between November 2010 and March 2011. 
To obtain(*ii*) plant abundance, we counted all units of floral atraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
We also recorded (*iii*) morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region. 
In addition we used data from the abundance counts 
Finally, to estimate the (*iv*) visit effectiveness, in addition to the visitation networks we need to construct pollen transfer networks. 
To construct the transfer networks we examined the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
In each of these visits we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.

>>>>

Our second objetive is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them, and (*iv*) the plants functional originality.
Here, we define visit efectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.

@@

To obtain the number of shared pollinators for each species (*i*), we collected data to construct qualitative and quantitative polination networks. 
Qualitative networks were constructed based on two hour observations of floral visits in each fragment. 
Quantitative networks were constructed using two 50 m randomly located transects in each transect. 
We counted and collected all floral visitors found in a 2 m wide strip while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999]. 
We visited the transects each month between November 2010 and March 2011. 
To obtain plant abundance (*ii*), we counted all units of floral atraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
To estimate visit effectiveness (*iii*), in addition to the visitation networks we need to construct pollen transfer networks. 
To construct the transfer networks we examined the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
Finally, We also recorded morphological traits (*iv*) that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region. 
Finally, 
More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
